Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-08-10 writeup/gz_hubble_data.tex
Necessary to get Manuscript Central's stupid system to accept PDF.
Reducing figure size for submitted MNRAS version
Fix typo in caption of Fig 8. Closes #181

@@

%\begin{figure*}
%\center
%\includegraphics[width=160mm]{figures/specz_comparison.pdf}
%\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogues.
%The number in the upper left of each plot is the percentage of redshifts which
%agree within $\Delta z < 0.05$ between the two catalogues being compared in each
%panel. Within this range there is over 98\% agreement in redshifts between all
%three catalogues.}
%\label{fig:speczs}
%\end{figure*}

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/gzh_interface.png}
\caption{Screenshot of the GZH interface at
the beginning of classifying a random galaxy, with the classifier ready
to select an answer for the first question in the decision
tree.\label{fig:interface}}
\end{figure*}

@@

\begin{figure}
\center
\includegraphics[width=0.5\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
includes only galaxies with a bounded range on the dropoff
($-10<\log(\zeta)<10$) and sufficient points to fit each function (37~original
galaxies, each artificially redshifted in eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$).}
\label{fig:zeta_mu}
\end{figure}

@@

%\begin{figure*}
%\center
%\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
%\caption{Distributions of redshift, surface brightness, and \ffeatures{} for
%correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full
%GZH sample. The lower-limit galaxies have higher redshifts, slightly lower
%surface brightness, and lower values of \ffeatures{} on average than the
%correctable galaxies. The long tail of NEI galaxies in redshift and surface
%brightness demonstrates the limits of the \ferengi{} sample, for which there
%is no data at $z>1$ or $\mu>24$.}
%\label{fig:z_mu_p}
%\end{figure*}

%\subsection{Results of \ferengi{} analysis}
%
%{\bf Old text from Taiwan workshop}
%
%We show here the preliminary results of GZH classifications of images of
%galaxies placed at artificial redshifts. Figure~\ref{fig:ferengi_results_fake}
%shows the range of change of vote fractions for the change of \ffeatures{}
%with redshift, for galaxies with different vote fraction levels, three ranges
%of surface-brightness levels and 7~evolutionary corrections (this last bit is
%indicated by the colour). 
%
%%---------------------------------------------------------------------------
%\begin{figure}
%\begin{center}
%
%\includegraphics[width=0.45\textwidth]{figures/somewhat_fake_results.pdf}
%
%\caption{Preliminary results of the \ferengi{} redshifting exercise. WARNING
%NO USER WEIGHTING.... For a range of vote fraction levels with three
%surface-brightness levels and 7 evolutionary corrections each (the colours
%indicate evolutionary correction value with green being $e=0$, we show the
%range of evolution of the vote fractions for featured vs. smooth with
%redshift.}
%
%\label{fig:ferengi_results_fake}
%
%\end{center}
%\end{figure}
%%--------------------------------------------------------------------------

@@

\section*{Acknowledgements}
KW, MG, CS, MB, and LF gratefully acknowledge support from the US National
Science Foundation Grant AST1413610. KS gratefully acknowledges support from
Swiss National Science Foundation Grant PP00P2\_138979/1. TM acknowledges
funding from the Science and Technology Facilities Council ST/J500665/1. The
development and hosting of Galaxy Zoo Hubble was supported by a grant from the
Alfred P. Sloan Foundation. The Zooniverse acknowledges support from a Google
Global Impact Award.

>>>>

\pdfminorversion 4

@@

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/gzh_interface.pdf}
\caption{Screenshot of the GZH interface at
the beginning of classifying a random galaxy, with the classifier ready
to select an answer for the first question in the decision
tree.\label{fig:interface}}
\end{figure*}

@@

\begin{figure}
\center
\includegraphics[width=0.5\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
includes only galaxies with a bounded range on the dropoff
($-10<\zeta<10$) and sufficient points to fit each function (37~original
galaxies, each artificially redshifted in eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$).}
\label{fig:zeta_mu}
\end{figure}

@@

@@

\section*{Acknowledgements}
KW, MG, CS, MB, and LF gratefully acknowledge support from the US National
Science Foundation Grant AST1413610. KS gratefully acknowledges support from
Swiss National Science Foundation Grant PP00P2\_138979/1. TM acknowledges
funding from the Science and Technology Facilities Council ST/J500665/1. 
RJS is supported by the STFC grant code ST/K502236/1.
The development and hosting of Galaxy Zoo Hubble was supported by a grant from
the Alfred P. Sloan Foundation. The Zooniverse acknowledges support from a
Google Global Impact Award.
